A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2023-05-18 discussion.tex
reorganized discussion

We believe our results can help researchers to create IDE tools for Rust. For instance, we discussed that \textit{Modifying the attributes of structs} is a common pattern that is observed in bug fix code changes. Assuming that the correct usage of attributes can be found other locations in the codebase~\citep{forrest2009genetic}, a code linter tool can be crafted to look for correct attribute lists.

Similarly, we presented the pattern \textit{Dropping clone and adding borrowing}. As discussed, Clippy does not detect this pattern, and repetitive clones can be computationally expensive and might lead to hogging the CPU. Using state-of-the-art methods for program repair, one could design a tool to recognize this pattern and change variable cloning to simple borrowing.

>>>>

\subsection{Usefulness of Rust Bug Patterns}

We believe our results can help researchers to create IDE tools for Rust. We have discussed the actionability of some of the general patterns and three BC-related patterns that are not detected by Clippy. For instance, we discussed considering the common pattern of \textit{Modifying the attributes of structs}, a code linter tool could be created to search for correct attribute lists within the codebase~\citep{forrest2009genetic}, leveraging the assumption that proper attribute usage can be found elsewhere. Also, the linter can analyze the usages of the struct to determine the necessity of adding the attribute. Removing unnecessary attributes not only optimizes the codebase but also eliminates unnecessary overhead and reduces the binary size. Similarly, we presented the pattern \textit{Dropping clone and adding borrowing}. As discussed, Clippy does not detect this pattern, and repetitive clones can be computationally expensive and might lead to hogging the CPU. Using state-of-the-art methods for program repair, one could design a tool to recognize this pattern and change variable cloning to simple borrowing. These findings and insights can greatly aid researchers in creating effective IDE tools tailored for Rust development. Moreover, the empirical frequency numbers associated with each pattern, highlighting its prevalence, can provide valuable guidance for the development of program repair tools.
